### 2022-07-22 main/chapter_2ljets.tex
more rework of zjets alt comparison

To avoid this extreme effect, I searched for alternative configurations
to the background model, such as constraining the parameter to $1$-sigma.
More senior members of the \atlas\ SUSY group decided that we should keep it as
described, reasoning along the lines that
a) this is a real and significant deficit in SR-Low that must appear as either
a pull on systematic variations or as a deviation from data, and
b) we prefer the pull on systematic variations.

With this decision, post-fit results, as presented in
Figure~\ref{fig:2ljets_summary},
indeed show no significant deviation from data in SR-Low-a or SR-Low-b,
and this $\zjets$ sample comparison is the main reason why.
Internal reviewers were, however, confused as to why we mentioned a deficit in
SR-Low that did not appear in the results plots or tables.
Much to my ire, all mentions of an SR-Low deficit were therefore removed from
the paper.
Despite bring real and significant, this deficit was erased from public view,
and to my knowledge it is only reported through the HistFactory models in our
HEPData~\cite{hepdata.116034}.

>>>>

It is not clear that such a large extrapolation from the difference between
two simulations is physically reasonable, especially since a large fraction
of its effect is due to the statistical error on a small alternative sample.
To avoid this questionable effect, I searched for alternative configurations
of the background model, such as constraining the parameter to $1$-sigma.
More senior members of the \atlas\ SUSY group decided that we should keep it as
described, reasoning along the lines that
a) this is a real and significant deficit in SR-Low, so must appear as either
a pull on systematic variations or as a deviation from data, and
b) we prefer the pull on systematic variations.

With this decision, post-fit results, such as the summary plot of
Figure~\ref{fig:2ljets_summary},
indeed show no significant deviation from data in SR-Low-a or SR-Low-b,
and this $\zjets$ sample comparison is the main reason why.
Internal reviewers were, however, confused as to why we mentioned a deficit in
SR-Low that did not appear in the results plots or tables.
Much to my ire, all mentions of an SR-Low deficit were therefore removed from
the paper.
Despite bring real and significant, this deficit was erased from public view,
and to my knowledge it is only reported through the HistFactory
models in our HEPData~\cite{hepdata.116034}.
